Preprocessing

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

# Journals data - exclusions

```{r}
d_journals_final_eligible <- d_journals_final %>%
  filter(journal_empirical == "Yes") %>%
  select(-journal_empirical)
```

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>%
  pivot_longer( # pivot to long format
    cols = c(-journal,-sample_id, -anyPPC,-general_note),
    names_to = c("PPC_type", ".value"), 
    names_sep = "_ppc_"
  )
```

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
         length_harmonized = str_remove(length_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         length_harmonized = case_when(
           length_harmonized == "1,000 words" ~ "1000",
           length_harmonized == "1,500 words (one figure and/or one table allowed within word count)" ~ "1500",
           length_harmonized == "1000 words" ~ "1000",
           length_harmonized == "16 pages" ~ as.character(16*pageToWord),
           length_harmonized == "2000 words" ~ "2000",
           length_harmonized == "265 lines of text including references" ~ as.character(265*linesToWord),
           length_harmonized == "3500 words (title page and references included)" ~ "3500",
           length_harmonized == "400 words" ~ "400",
           length_harmonized == "5 pages, including abstract, references, tables, and figures." ~ as.character(5*pageToWord),
           length_harmonized == "500 words" ~ "500",
           length_harmonized == "600-800 words" ~ "800",
           length_harmonized == "750 words" ~ "750",
           length_harmonized == "Approx. 1,000 words" ~ "1000",
           length_harmonized == "approximately 1,000 words" ~ "1000",
           length_harmonized == "as concise as possible, and ideally not exceed 1,200 words" ~ "1200",
           length_harmonized == "at maximum half the length of the target article." ~ "Qualitative",
           length_harmonized == "Maximum length: 1100 words." ~ "1100",
           length_harmonized == "short" ~ "Qualitative",
           length_harmonized == "up to 2,000 words counting 500 words per table and figure" ~ "2000",
           TRUE ~ length_harmonized
         )) 
```

>>>>

@@

```{r}
d_journals_final <- d_journals_final %>%
  pivot_longer( # pivot to long format
    cols = c(-journal,-journal_empirical,-sample_id,-anyPPC,-general_note),
    names_to = c("PPC_type", ".value"), 
    names_sep = "_ppc_"
  )
```

@@

```{r}
d_journals_final <- d_journals_final %>% 
  mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
         length_harmonized = str_remove(length_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         length_harmonized = case_when(
           length_harmonized == "1,000 words" ~ "1000",
           length_harmonized == "1,500 words (one figure and/or one table allowed within word count)" ~ "1500",
           length_harmonized == "1000 words" ~ "1000",
           length_harmonized == "16 pages" ~ as.character(16*pageToWord),
           length_harmonized == "2000 words" ~ "2000",
           length_harmonized == "265 lines of text including references" ~ as.character(265*linesToWord),
           length_harmonized == "3500 words (title page and references included)" ~ "3500",
           length_harmonized == "400 words" ~ "400",
           length_harmonized == "5 pages, including abstract, references, tables, and figures." ~ as.character(5*pageToWord),
           length_harmonized == "500 words" ~ "500",
           length_harmonized == "600-800 words" ~ "800",
           length_harmonized == "750 words" ~ "750",
           length_harmonized == "Approx. 1,000 words" ~ "1000",
           length_harmonized == "approximately 1,000 words" ~ "1000",
           length_harmonized == "as concise as possible, and ideally not exceed 1,200 words" ~ "1200",
           length_harmonized == "at maximum half the length of the target article." ~ "Qualitative",
           length_harmonized == "Maximum length: 1100 words." ~ "1100",
           length_harmonized == "short" ~ "Qualitative",
           length_harmonized == "up to 2,000 words counting 500 words per table and figure" ~ "2000",
           TRUE ~ length_harmonized
         )) 
```
